Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-11 paper.qmd
Initial work on the table

>>>>

Direct links to videos for viewing online are available in @tbl-links.

```{r}
#| label: tbl-links
#| tbl-cap: "Example videos."
#| tbl-pos: H

links_df <- tibble(
  data = c("PBMC3k"),
  URL = c("link1")
)

links_df |>
  kableExtra::kable(format = "latex", 
                    booktabs = TRUE, 
                    label = "tbllinks") |>
  kableExtra::kable_styling(latex_options = "scale_down")
